\begin{acknowledgments}     % optional acknowledgments      
                                                                                                         
First, I thank my advisor Maria Spiropulu. Her
wisdom, experience, and warmth have shaped me as I've
developed as a scientist. For her endless contributions to my life
and career, I am in her debt.

I thank Maurizio Pierini for his intense mentorship beginning at CERN
in 2011 and continuing to this day. Maurizio taught me how to be a
modern particle physicist, by sharing his expertise in computing, statistics, and
phenomenology. He was also invaluable in helping me prepare this manuscript.

I also thank Chris Rogan for guiding me during my first days of
graduate school and for being a good friend. Cristi\'{a}n Pe\~{n}a and
Dustin Anderson have been constant friends and fellow soldiers in
graduate school. I thank my other colleagues in the Caltech CMS group
for their help and advice during graduate school: Si Xie, Artur
Apresyan, Jean-Roch Vlimant, and Adi Bornheim.

I thank my roommates and close friends: Ingmar Saberi, Tristan McKinney,
Eric Quintero, and Evelyn Gomez. They continually inspire me and
remind me to have fun every once in a while. 
I also thank the other two legs of our marathon running team, Alex Tuna and Phil Hebda, for their friendship,
which has spanned many years and two continents, and for constantly challenging
me to improve my marathon PR.

I dedicate this thesis to my mother, Bruny, and my sister, Rossy, for
loving and supporting me throughout my life.

Finally, I thank my girlfriend Kristen Jezior. Without her love,
kindness, and humor, I would be lost.

\end{acknowledgments}